### 2020-04-23 final_report/data.tex
harmonise run time notation

\begin{table}[h]
	\sisetup{round-mode=places,round-precision=2}
	\centering
	{\footnotesize
		\begin{tabular}{rlllll}
		\toprule
		\#	& Samples & Batch division & Total run time & MET [\si{\second}] & Description \\
		\midrule
		0 & \num{100000} & $\num{100}\times\num{1000}$ & 2~days, 23~h 
		  & $\num{7.877122043981347} \pm \num{2.749485948560108}$ &
		Testing run using older MC TBR version.\\
		1 & \num{500000} & $\num{500}\times\num{1000}$ & 13~days, 20~h
		  & $\num{7.777049573054314} \pm \num{2.8103592103930337}$ &
		Fully uniform sampling in the entire domain.\\
		2 & \num{400000} & $\num{400}\times\num{1000}$ & 10~days 
		  & $\num{7.944379778103232} \pm \num{2.601428571503671}$ &
		Mixed sampling, discrete features fixed.\\
		\bottomrule
		\end{tabular}
	}
	\caption{Parameters of sampling runs. Total run time includes waiting in
	the processing queue. MET stands for mean evaluation time (per single
	sampled point).}
	\label{tbl:sampling-runs}
\end{table}

@@

\begin{table}[h]
	\centering
	{\footnotesize
		\begin{tabular}{r|lllllll}
		\toprule
		{} & \multicolumn{7}{c}{Discrete feature assignment}\\
		Batches & BBM & BCM & BMM & BSM & FAM & FCM & FSM \\
		\midrule
		0-99 & \ce{Li4SiO4} & \ce{H2O} & \ce{Be12Ti} & eurofer & tungsten & \ce{H2O} & eurofer\\
		100-199 & \ce{Li4SiO4} & \ce{He} & \ce{Be12Ti} & eurofer & tungsten & \ce{H2O} & eurofer\\
		200-299 & \ce{Li4SiO4} & \ce{H2O} & \ce{Be12Ti} & eurofer & tungsten & \ce{He} & eurofer\\
		300-399 & \ce{Li4SiO4} & \ce{He} & \ce{Be12Ti} & eurofer & tungsten & \ce{He} & eurofer\\
		\bottomrule
		\end{tabular}
	}
	\caption{Selected discrete feature assignments corresponding to slices in run~2.}
	\label{tbl:slices}
\end{table}

>>>>

\begin{table}[h]
	\sisetup{round-mode=places,round-precision=2}
	\centering
	{\footnotesize
		\begin{tabular}{rlllll}
		\toprule
		\#	& Samples & Batch division & $t_{\text{run}} $ 
			& $\overline{t}_{\text{eval.}}$ [\si{\second}] & Description \\
		\midrule
		0 & \num{100000} & $\num{100}\times\num{1000}$ & 2~days, 23~h 
		  & $\num{7.877122043981347} \pm \num{2.749485948560108}$ &
		Testing run using older MC TBR version.\\
		1 & \num{500000} & $\num{500}\times\num{1000}$ & 13~days, 20~h
		  & $\num{7.777049573054314} \pm \num{2.8103592103930337}$ &
		Fully uniform sampling in the entire domain.\\
		2 & \num{400000} & $\num{400}\times\num{1000}$ & 10~days 
		  & $\num{7.944379778103232} \pm \num{2.601428571503671}$ &
		Mixed sampling, discrete features fixed.\\
		\bottomrule
		\end{tabular}
	}
	\caption{Parameters of sampling runs. Here, $t_{\text{run}}$ denotes the total run
		time (including waiting in the processing queue), and
		$\overline{t}_{\text{eval.}}$ is the mean evaluation time of MC TBR (per single
		sampled point).}
	\label{tbl:sampling-runs}
\end{table}

@@

\begin{table}[h]
	\centering
	{\footnotesize
		\begin{tabular}{rlllllll}
		\toprule
		{} & \multicolumn{7}{c}{Discrete feature assignment}\\
		\cmidrule(lr){2-8}
		Batches & BBM & BCM & BMM & BSM & FAM & FCM & FSM \\
		\midrule
		0-99 & \ce{Li4SiO4} & \ce{H2O} & \ce{Be12Ti} & eurofer & tungsten & \ce{H2O} & eurofer\\
		100-199 & \ce{Li4SiO4} & \ce{He} & \ce{Be12Ti} & eurofer & tungsten & \ce{H2O} & eurofer\\
		200-299 & \ce{Li4SiO4} & \ce{H2O} & \ce{Be12Ti} & eurofer & tungsten & \ce{He} & eurofer\\
		300-399 & \ce{Li4SiO4} & \ce{He} & \ce{Be12Ti} & eurofer & tungsten & \ce{He} & eurofer\\
		\bottomrule
		\end{tabular}
	}
	\caption{Selected discrete feature assignments corresponding to slices in run~2.}
	\label{tbl:slices}
\end{table}
